\vspace{-2cm} Content of Municipal Government Websites

### 2017-03-27 paper/manuscript.tex
update manuscript

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Mar 24 12:21:19 2017
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
File type & oct15 & jan16 & feb16 & mar16 \\ 
  \hline
.pdf & 358 & 183 & 111 & 394 \\ 
  .aspx &  99 & 112 & 116 &  76 \\ 
  .jpg &  22 &  24 &  17 &  12 \\ 
  .gif &   3 &   5 &   1 &   5 \\ 
  .JPG &   3 &   2 &   1 &   5 \\ 
  .png &   3 &   7 &   2 &   1 \\ 
  .asmx &   2 &   1 &   1 &   5 \\ 
  .PDF &   1 &   1 &   1 &   2 \\ 
   \hline
\end{tabular}
\caption{File types of Indy.gov at different points in time} 
\end{table}

>>>>

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Mar 24 12:52:43 2017
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
File type & oct15 & jan16 & feb16 & mar16 \\ 
  \hline
.pdf & 179 & 183 & 111 & 197 \\ 
  .aspx &  99 & 112 & 116 &  76 \\ 
  .jpg &  22 &  24 &  17 &  12 \\ 
  .gif &   3 &   5 &   1 &   5 \\ 
  .JPG &   3 &   2 &   1 &   5 \\ 
  .png &   3 &   7 &   2 &   1 \\ 
  .asmx &   2 &   1 &   1 &   5 \\ 
  .PDF &   1 &   1 &   1 &   2 \\ 
   \hline
\end{tabular}
\caption{File types of Indy.gov at different points in time} 
\end{table}
